paper

### 2019-01-11 Report/paper.tex
push paper

As there are a variety of way in which the name of an institution could
be written --consider EPFL, EPF Lausanne-- crawling the english, french
and german version of Wikipedia (not using the API, or the API wrapper,
as this does not give access to the desired information) was a quick and
accurate way to get the location. The advantage of sending requests over
using the API is due to the website redirecting to the relevant article
on the institution even when misspellings are present. Requests were
sent using \emph{urllib3} and \emph{beautifulsoup} was used to parse
them get the coordinates present in the article. Regretfully not all
institutions, even well known ones such as Tokyo University, have their
coordinates listed on Wikipedia. To get the remaining locations we used
the geopy, which is a client for geocoding web services. These results
however are more error prone and will always return a result. It is thus
recommended to verify the correctness of the results. To get the country
we then again used geopy. The resulting data containing paper
identifier, the authors email, its associated domain, order in which the
author was cited, the institution, country, Longitude and Latitude were
saved to a csv file. We used the paper identifier and author order to
associate this data with the metadata to link information about authors
with the papers they authored.

@@

    \hypertarget{methodology-find-better-section-head..}{%
\section{Methodology {[}find better section
head..{]}}\label{methodology-find-better-section-head..}}

>>>>

As there are a variety of way in which the name of an institution could
be written --consider EPFL, EPF Lausanne-- crawling the english, french
and german version of Wikipedia (not using the API, or the API wrapper,
as this does not give access to the desired information) was a quick and
accurate way to get the location. The advantage of sending requests over
using the API is due to the website redirecting to the relevant article
on the institution even when misspellings are present. Requests were
sent using \emph{urllib3} and \emph{beautifulsoup} was used to parse
them get the coordinates present in the article. Regretfully not all
institutions, even well known ones such as Tokyo University, have their
coordinates listed on Wikipedia. To get the remaining locations we used
the geopy, which is a client for geocoding web services. These results
however are more error prone and will always return a result. It is thus
recommended to verify the correctness of the results. To get the country
we then again used geopy. The resulting data containing paper
identifier, the authors email, its associated domain, order in which the
author was cited, the institution, country, longitude and latitude were
saved to a csv file. We used the paper identifier and author order to
associate this data with the metadata to link information about authors
with the papers they authored.

@@

    \hypertarget{methods-for-data-analysis}{%
\section{Methods for Data Analysis}\label{methods-for-data-analysis}}
